\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{enumitem}

\geometry{a4paper, margin=0.75in}

\begin{document}

\title{\textbf{DBMS Project Overview: Gada Electronics Online Retail Store}}
\author{Group 10 \\ Vikranth Udandarao, Tharun Harish, Hemanth Dindigullu, Aditya Prasad}
\date{}
\maketitle

\section*{Project Scope}
Gada Electronics Online Retail Store aims to create an efficient online platform offering a diverse range of electronic products. Customers can seamlessly browse, purchase, and track orders. Warehouse managers have tools to manage inventory effortlessly. The system integrates loyalty programs and location-based trends for an enhanced user experience.

\section*{Functional Requirements}

\subsection*{Customer Module}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Sign Up / Login:}
          \begin{itemize}
              \item Customers can create accounts using their name, email, phone number, and a password.
              \item Login using email/phone and password and then add or select the address.
          \end{itemize}
    \item \textbf{View Products:}
          \begin{itemize}
              \item Customers can browse products categorized into different electronic types (Laptops, Mobile Phones, etc.).
          \end{itemize}
    \item \textbf{Add to Cart:}
          \begin{itemize}
              \item Customers can add products to their cart for future purchase.
          \end{itemize}
    \item \textbf{Payment:}
          \begin{itemize}
              \item Customers can make payments for their orders.
          \end{itemize}
    \item \textbf{Buy:}
          \begin{itemize}
              \item Confirm and complete the purchase.
          \end{itemize}
\end{enumerate}

\subsection*{Warehouse Manager Module}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Sign Up / Login:}
          \begin{itemize}
              \item Warehouse managers can create accounts using their name, email, phone number, and a password.
              \item Login using email/phone and password.
          \end{itemize}
    \item \textbf{Manage Products:}
          \begin{itemize}
              \item Add, update, and delete products.
              \item Update product descriptions.
          \end{itemize}
\end{enumerate}

\section*{Features}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Loyalty:}
          \begin{itemize}
              \item Implement a loyalty program to reward repeat customers.
          \end{itemize}
    \item \textbf{Location-Based Trends:}
          \begin{itemize}
              \item Analyze customer data to provide location-based product recommendations and discounts.
          \end{itemize}
\end{enumerate}

\section*{Database Entities}

\subsection*{Customer Entity}
\begin{itemize}
    \item \textbf{CustomerID (Primary Key)}
    \item Name
    \item Email
    \item Phone no
    \item Passwor

\end{itemize}

\subsection*{Address Entity}
\begin{itemize}
    \item \textbf{AddressID (Primary Key)}
    \item \textbf{CustomerID (Foreign Key)}
    \item Address detail

\end{itemize}

\subsection*{Product Entity}
\begin{itemize}
    \item \textbf{ProductID (Primary Key)}
    \item Manufacturer
    \item Name
    \item Price
    \item Description
    \item Quantity
    \item Discount

\end{itemize}

\section*{Technical Requirements}
\begin{itemize}
    \item We plan on using HTML, CSS, and JavaScript languages for the front end.
    \item We plan on using Flask and Python for the back end.
    \item We plan on using MySQL for the database.

\end{itemize}

\end{document}
