\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{enumitem}

\geometry{a4paper, margin=0.5in}

\begin{document}

\title{\textbf{DBMS Project Overview\\ Gada Electronics Online Retail Store}}
\author{Group 10 \\ Vikranth Udandarao - 22570, Tharun Harish - 22541,\\ Hemanth Dindigallu - 22212, Aditya Prasad - 22036}
\date{}
\maketitle

\section*{Project Scope}
Gada Electronics Online Retail Store aims to create an efficient online platform offering a diverse range of electronic products. Customers can seamlessly browse, purchase, and track orders. Warehouse managers have tools to manage inventory effortlessly. The system integrates loyalty programs and location-based trends for an enhanced user experience.

\section*{Functional Requirements}

\subsection*{Customer Module}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Sign Up / Login:}
          \begin{itemize}
              \item Customers can create accounts using their name, email, phone number, and a password.
              \item Login using email/phone and password and then add or select the address.
          \end{itemize}
    \item \textbf{View Products:}
          \begin{itemize}
              \item Customers can browse products categorized into different electronic types (Laptops, Mobile Phones, etc.).
          \end{itemize}
    \item \textbf{Add to Cart:}
          \begin{itemize}
              \item Customers can add products to their cart for future purchase.
          \end{itemize}
    \item \textbf{Payment:}
          \begin{itemize}
              \item Customers can make payments for their orders.
          \end{itemize}
    \item \textbf{Buy:}
          \begin{itemize}
              \item Confirm and complete the purchase.
          \end{itemize}
\end{enumerate}

\subsection*{Warehouse Manager Module}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Sign Up / Login:}
          \begin{itemize}
              \item Warehouse managers can create accounts using their name, email, phone number, and a password.
              \item Login using email/phone and password.
          \end{itemize}
    \item \textbf{Manage Products:}
          \begin{itemize}
              \item Add, update, and delete products.
              \item Update product descriptions.
          \end{itemize}
\end{enumerate}

\section*{Features}
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Loyalty:}
          \begin{itemize}
              \item Implement a loyalty program to reward repeat customers.
          \end{itemize}
    \item \textbf{Location-Based Trends:}
          \begin{itemize}
              \item Analyze customer data to provide location-based product recommendations and discounts.
          \end{itemize}
\end{enumerate}

\section*{Database Entities}

\subsection*{Customer Entity}
\begin{itemize}
    \item \textbf{CustomerID (Primary Key)}, Name, Email, Phone no, Password

\end{itemize}

\subsection*{Address Entity}
\begin{itemize}
    \item \textbf{AddressID (Primary Key)}, \textbf{CustomerID (Foreign Key)}, Address detail

\end{itemize}

\subsection*{Product Entity}
\begin{itemize}
    \item \textbf{ProductID (Primary Key)}, Manufacturer, Name, Price, Description, Quantity, Discount

\end{itemize}

\section*{Technical Requirements}
\begin{itemize}
    \item \textbf{Front End}: HTML, CSS, JavaScript
    \item \textbf{Back End}: Flask, Python
    \item \textbf{Database}: MySQL

\end{itemize}

\end{document}